Insert the article title here

### 2020-07-23 tex/results.tex
Add more writing on grid independance study

%%% Rockstuhl work summary%%%%
The work of Rockstuhl et al. study the phonon-polariton response of silicon carbide (SiC)
nanoparticles using the boundary element method. They analyze different "cylindrical particles"
made of 6H-SiC as a function of geometrical cross section. These "cylinders" have an infinite
extension in the third dimension, and they solve these geometries numerically with a 2D 
boundary element method from their previous work \cite{rockstuhl2003}. 
%%% Rockstuhl work summary%%%%

We decided to replicate one of the results that they present on Fig.14 of their paper, which 
presents the scattering cross section of a SiC rectangular cylinder for three different object 
sizes. To complain with our quasistatic approach we chose the particular case where a=672 nm and 
b=328 nm.

\textbf{difference between methods, mesh and dielectric data}

\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem, 
while we solve a 3D model. In our case the geometry has a finite third dimension. To cope with this
we will extend the third direction considerably, and study this effect.

@@

These first set of results correspond to the replication study of some results 
of Rockstuhl et al, 2005 \cite{rockstuhl2005}. Rockstuhl and coworkers did a two dimension 
study of the phonon-polariton response of different nanoparticles of silicon carbide (SiC)
using a 2D boundary element method. Their limit their study to 2D shapes and assumed an infinite
third dimension. (They solved full maxwell in 2D)

We count with a 3D surface boundary element method solver, that uses the electrostatic approximation
($\lambda > d$ where $d$ is the characteristic length of the geometry).

{\color{red}We initially produced the meshes with trimesh (not sure how to cite), later we stick to 
our own script}

Initially we attempted to perform a convergence study on the result of Figure 18a
of Rockstuhl and coworkers. This simulation consists on a "quadratic cylinder" (square)
of size $L=535$. We tried to perform convergence on a cube of the same size L, but
due to the due to the sharp edges of the geometry we were not able to see proper convergence. 
However, we did a grid independence study. We were able to show that going from a mesh of 15552 
triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
triangles the simulations did not change at all (see Figure \ref{fig:cube535}).

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid independence study for a SiC cube of side L=535 nm, in air under a constant 
    electric field in the z-direction. Extinction cross section divided by $L^2$ as a function of wavelength divided 
    by $L$ of a cube of size L=535 nm}
    \label{fig:cube535}
 \end{figure}

In this results we see extra peaks that we believe is due to the nature of our 3D model, in this case 
we have not extended the third dimension to approximate "infinity", but we suspect the extra peaks are 
due to sharpness of the edges (they mention this on their paper too) as well as the 3D nature of our solver.

These figure doesn't have the results digitized from the paper, but if needed we can add them.

Based on these results we used the density of the cube as a reference to produce the meshes for the replication 
of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). This simulation is a "rectangular cylinder" of 
dimensions (we chose a case that will go well with our quasistatic model) are $a=672$ nm and $b=328$ nm.

>>>>

%%% Rockstuhl work summary%%%%
The work of Rockstuhl et al.\cite{rockstuhl2005} study the phonon-polariton response of silicon carbide (SiC)
nanoparticles using the boundary element method. They analyze different "cylindrical particles"
made of 6H-SiC as a function of geometrical cross section. These "cylinders" have an infinite
extension in the third dimension, and they solve these geometries numerically with a 2D 
boundary element method from their previous work \cite{rockstuhl2003}. 
%%% Rockstuhl work summary%%%%

We decided to replicate one of the results that they present on Fig.14 of their paper, which 
presents the scattering cross section of a SiC rectangular cylinder for three different object 
sizes. To complain with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
case where a=672 nm and b=328 nm.

\textbf{Difference between methods, mesh and dielectric data}

\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem, 
while we solve a 3D model. In our case the geometry has a finite third dimension. To cope with this
we will extend the third direction considerably, and study this effect.
We compute extinction cross section (scattering plus absorption) while Rockstuhl work present only scattering. 
But since in both scattering and absorption the resonance occur at the same wavelengths, the results are 
comparable.

@@

\subsubsection{Grid independance study}

We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the z-axis.
(similar to quadratic cylinder on Fig 18 of Rockstuhl et.al). 
Due to the nature of the geometry, and its sharp edges it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiCooperBarba2019}. 
In the Figure \ref{fig:cube535} we show a grid independence study, where we go from a mesh of 15552 
triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
triangles and the computed results do not change.

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
    electric field in the z-direction. The curves represent the extinction cross section divided by $L^2$ 
    as a function of wavelength divided by $L$}
    \label{fig:cube535}
 \end{figure}

It is worth noting that the extinction cross section curve in Figure \ref{fig:cube535} has extra peaks, 
compared to the results of Figure 18 on Rockstuhl, this is due to the 3D nature of our case and the sharp 
edges. This will be approach in the following results where we attempt a replication of one of teh results 
of Figure 14 of Rockstuhl work.

\subsubsection{Replication of Figure 14 (case a1) of Rockstuhl 2005}

Based on the reuslts of the grid independence stud we decided to we used the density of the cube as a reference to produce the meshes for the replication 
of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). This simulation is a "rectangular cylinder" of 
dimensions (we chose a case that will go well with our quasistatic model) are $a=672$ nm and $b=328$ nm.
